Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021

### 2021-06-19 paper/paper.tex
Update

The eHealth-KD task focuses on cross-domain, multi-lingual and low-resource solutions. This setting presents a significant challenge to existing state-of-the-art methods, which often rely on large amounts of training data.
A succesful approach to the eHealth-KD must leverage transfer learning across both different domains and languages, since the vast majority of the training examples are provided in Spanish language and Medline articles, while only a small development set is available in the remaining settings.
With this added complexity, we expect to encourage solutions that can be deployed in low-resource environments, where is unfeasible to train large language models over longs periods of time.

@@

  \item[Maoqin:]  Several deep learning models are used in plain text documents, such as
  BERT-CRF, BiLSTM-CRF. Only the best result running in the local has been submitted. But the final
  result of my method is indeed very low, with a score of 0.173 (F1), ranking 9th on the leaderboard.
  Additional work needs to be done to improve our final result and complete the subtask B: relation
  extraction.

  \item[Maoquin:] For one method, the pre-trained BERT model has been taken as the basic representation.
  For another method, BiLSTM has been preferred. The system achieved unsatisfied results in the
  challenge for official evaluation in subtask A. Due to the colab’s time and resources limitation,
  some strategies were not achieved. And subtask B: Relation Extraction has not been completed.

>>>>

The eHealth-KD task focuses on cross-domain, multi-lingual and low-resource solutions. This setting presents a significant challenge to existing state-of-the-art methods, which often rely on large amounts of training data.
A succesful approach to the eHealth-KD must leverage transfer learning across different domains and languages, since the vast majority of the training examples are provided in Spanish language and from the Medline domain, while only a small development set is available in the remaining settings.
With this added complexity, we expect to encourage solutions that can be deployed in low-resource environments, where is unfeasible to train large language models over longs periods of time.

@@

  \item[Maoqin:]  Several deep learning models are used in plain text documents, such as
  BERT-CRF, BiLSTM-CRF. Only the best result running in the local has been submitted. But the final
  result of my method is indeed very low, with a score of 0.173 (F1), ranking 9th on the leaderboard.
  Additional work needs to be done to improve our final result and complete the subtask B: relation
  extraction. For one method, the pre-trained BERT model has been taken as the basic representation.
  For another method, BiLSTM has been preferred. The system achieved unsatisfied results in the
  challenge for official evaluation in subtask A. Due to the colab’s time and resources limitation,
  some strategies were not achieved. And subtask B: Relation Extraction has not been completed.
